Type Ia Supernova Explosions from Hybrid Carbon-Oxygen-Neon White Dwarf Progenitors

### 2018-12-07 paper/ms.tex
More on Carlyn's paper

The single degenerate picture posits a white dwarf gaining mass
from a main-sequence companion. The process relies on a long
period of accretion combined with either steady burning or a 
series of nova explosions to allow the WD to gain
~0.6 CHECK THIS \Msun needed for it to approach the
limiting Chandrasekhar mass~\citep{starrfieldetal2012}. As it approaches
the Chandrasekhar limit, conditions in the compressed core are right
to ignite the thermonuclear buring that will incinerate the star. Within this
progenitor setting, the models that best reproduce the observed
stratified ejecta are those in which the burning begins as a 
subsonic deflagration, which allows the star to react and expand
thus lowering the density, that is followed by a 
detonation~\citep{Nomo84,Khokhlov1991Delayed-detonat,HoefKhok96,GameKhokOran05}.
We adopt this setting for the explosion simulations we present and 
describe our approach in detail below.

@@

\subsection{The near-Chandrasekhar-mass Single Degenerate Scenario}

@@

>>>>

The single degenerate picture posits a white dwarf gaining mass
from a main-sequence companion. The process relies on a long
period of accretion combined with either steady burning or a 
series of nova explosions to allow the WD to gain
~0.6 CHECK THIS \Msun needed for it to approach the
limiting Chandrasekhar mass~\citep{starrfieldetal2012}. As it approaches
the Chandrasekhar limit, conditions in the compressed core are right
to ignite the thermonuclear buring that will incinerate the star.

Within this progenitor setting, many mechanisms for the explosion have 
been studied with the result being that the outcome is sensitive to
the ignition conditions and the nature of the thermonuclear buring.
Studies indicate that neither a pure deflagration (subsonic flame front)
nor a pure detonation (supersonic burning front) produce ejecta conisitent
with observations \citep{arnett69,roepkeetal07}.
Instead, the models that best reproduce the observed
stratified ejecta are those in which the burning begins as a 
subsonic deflagration, which allows the star to react and expand
thus lowering the density, that is followed by a 
detonation~\citep{Nomo84,Khokhlov1991Delayed-detonat,HoefKhok96,GameKhokOran05}.
The classic delayed detonation model is that of 
Khokhlov \cite{Khokhlov1991Delayed-detonat,hoflich.khokhlov.ea:delayed,GameKhokOran05},
and many variations have been 
explored \cite[and references therein]{hillebrandtetal2013,calderetal2013}.
The approach we employ for this study is a variation, the deflagration-to-detonation
transition (DDT).

@@

\subsection{The Deflagraiton to Detonation Transition Mechanism Within the Single Degenerate Scenario}

Our models are within the DDT explosion paradigm \cite{1986SvAL,
Khokhlov1991Delayed-detonat,NiemWoos97,Niem99,belletal2004, fishjump2015}. 
Thermonuclear burning begins as a deflagration in the core of the WD.
The flame is unstable, and as the deflagration propagates toward the surface
of the WD, it is subject to the Rayleigh-Taylor instability that generates
turbulence and boosts buring.  
Burning proceeds as a deflagration

and we 
adopt a variation of the latter case, a deflagration-to-detonation transition
that occurs at the top of a rising plume of hot, burned material when it
reaches a threshold density.

Because the two extremes of pure deflagrations or pure detonations cannot
robustly reproduce events with characteristics consistent with the observations,
researchers have investigated models evoking a combination of the two. These models
may be broadly described as delayed detonation, and a variety of scenarios have
been proposed. The classic delayed detonation model was introduced by
Khokhlov \cite{Khokhlov1991Delayed-detonat,hoflich.khokhlov.ea:delayed,GameKhokOran05},
and variations include pulsational
detonations \cite{ivanovaetal1974,Khokhlov1991Delayed-detonat,
arnettlivne94a, arnettlivne94b, bravogarcia-senz2006},
gravitationally confined detonation \cite{PlewCaldLamb04,Jordan2008Three-Dimension,
jordanetal2012}, and deflagration-to-detonation
transitions (DDTs) \cite{1986SvAL,Khokhlov1991Delayed-detonat,NiemWoos97,Niem99,belletal2004,
fishjump2015}. We adopt a variation of the latter case, a deflagration-to-detonation transition
that occurs at the top of a rising plume of hot, burned material when it
reaches a threshold density.

The physics by which a DDT may occur are not completely understood, but
ideas have been proposed. One idea is that at low densities the flame
enters a regime of distributed burning in which it is no longer
well-defined but the net burning rate is high enough that it is
effectively supersonic \cite{NiemWoos97}. Similarly, others argue
that when the flame reaches a certain fractal dimension, it is
effectively supersonic \cite{woosley90}. The Zel'dovich mechanism
posits that composition and temperature gradients may ``prepare" the
fuel in just the right way that it will detonate
\cite{zeldovichetal1970,KhokOranWhee97,jacketal2014}. Our approach
is to assume that when the top of a rising, Rayleigh-Taylor unstable
plume reaches a particular density, conditions are favorable and the
transition occurs \cite{townsley.calder.ea:flame}.

@@

Recent population synthesis work indicating a substantial contribution
to the Ia population rate from mergers where one member is a 
hybrid~\citep{yungelsonkuranov2017}.
